Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-05-12 main.Rmd
Fig 3 caption revised

(ref:aperiodic-example) Quasi-circular and aperiodic cyclic granularities illustrated through (a) linear and (b) stacked displays of time. The linear display shows granularities days ($B$), weeks ($G$), semester days ($B'$), and stages of a semester ($M$) distributed over linear time. Granules of $B'$ is only defined for days when the semester is running. Here a semester lasts for 18 weeks and 2 days, each consisting of 5 stages. It starts with an orientation stage, followed by a first stage of the in-session period (6 weeks), a break (1 week), a second stage of the in-session period (7 weeks), a 1-week study break stage, before final exams stage which continue for 16 days. This distribution of semester days within a semester remains the same for every semester and hence $Q_{B', M}$ with $P$ = 128 days will be a quasi-circular granularity with repeating patterns. $A_{B, M}$ will be an aperiodic cyclic granularity since 
the placement of the semester within a year varies across years and there is no definite number of days after which the semester begins every year.

>>>>

(ref:aperiodic-example) Quasi-circular and aperiodic cyclic granularities illustrated by linear (a) and 
stacked-displays (b) progression of time. The linear display shows the granularities days ($B$), weeks ($G$), semester days ($B'$), and stages of a semester ($M$) indexed over a linear representation of time. The granules of $B'$ is only defined for days when the semester is running. Here a semester spans 18 weeks and 2 days, and consists of 6 stages. It starts with a week of orientation, followed by an in-session period (6 weeks), a break (1 week), the second half of semester (7 weeks), a 1-week study break before final exams, which spans the next 16 days. This distribution of semester days remains relatively similar for every semester. $Q_{B',M}$ with P = 128 is a quasi-circular granularity with repeating patterns, while $A_{B,M}$ is an aperiodic cyclic granularity as the placement of the semester within a year varies from year to year with no fixed start and end dates.
